\documentclass[a4paper,11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{fontenc}
\usepackage{fontawesome5}

\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}


\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\itshape}{}{0em}{}

\begin{document}
{\fontfamily{qhv}\selectfont
\begin{center}
    {\LARGE \textbf{Yousef Refaat Elmasry}}\\
\end{center}

\section*{ {\faAddressBook} Contact Information}
\begin{itemize}
    \item \textbf{Email:} {\faEnvelope} \href{mailto:Yousef000elmasry@gmail.com}{yousef000elmasry@gmail.com}
    \item \textbf{Phone:} {\faPhone +201228899932 / +966595725131
    \item \textbf{LinkedIn:} {\faLinkedin} \href{https://www.linkedin.com/in/yousef-refaat-1597a5172}{linkedin.com/in/yousef-refaat-1597a5172}
    \item \textbf{Blogs:} {\faParagraph} \href{https://dev.to/yrafe}{dev.to/yrafe}
\end{itemize}



\section*{{\faUserTie} Summary}
Passionate and experienced Software Engineer with a strong background in backend and full-stack development. Skilled in Java, Spring Boot, Angular, Microservices, and cloud technologies. Experienced with designing scalable architectures, integrating modern authentication mechanisms, and working with event-driven systems. Strong debugging and problem-solving abilities, with experience leading projects and mentoring junior developers.
\section {{\faBriefcase} Work Experience}
\subsection*{ MicroServices Developer  \textbar{} Saudi Investment Bank (Sumerge) (July 2024 - Present)}
\subsection*{ Software Engineer \textbar{} Sumerge (September 2021 – Present)}
\section*{{\faStar} Skills}
\begin{itemize}
    \item \textbf{Programming:} Java, JavaScript, TypeScript
    \item \textbf{Frameworks:} Spring Boot, Angular, React, Liferay, IBM BPM, Apache Camel
    \item \textbf{Databases:} SQL, NoSQL, JPA, JOOQ
    \item \textbf{DevOps \& Cloud:} Docker, Kubernetes, Redhat Openshift, AWS, Jenkins
    \item \textbf{Event-Driven \& Messaging:} Kafka, JMS
    \item \textbf{Other:} OAuth2, Keycloak, Redis, GraphQL, CI/CD, REST APIs, Microservices, BPM \& Workflow Automation
\end{itemize}

\section*{{\faPen} Projects}

\subsubsection*{Retail Internet Banking \textbar{} Saudi Investment Bank - KSA (Mar 2023 – Aug 2023, Aug 2024 – Present)}
\begin{itemize}
\item \textbf{GraphQL} Acting as an API Gateway to  expose business services with flexible querying and aggregation.
\item \textbf{Service-Oriented Layer} implements business logic and orchestrates domain-specific services.
\item \textbf{Enterprise Integration Layer (Apache Camel)} to handle message routing, transformation, protocol bridging, and communicate with Core Banking Systems

    \item Worked extensively with \textbf{Spring Boot, MongoDB, JMS, BeanIO, Strapi, and REST APIs}.
    \item Gained deeper insights into \textbf{Java Core (Servlets \& JVM), OAuth flows, networking, and AWS}.
        \item Worked on several domains including \textbf{Credit, Transactions, Accounts, KYC}, and \textbf{Onboarding}
\end{itemize}

\subsubsection*{Loyalty Platform \textbar{} Etisalat - Egypt (Oct 2023 – July 2024)}
\begin{itemize}
    \item Built a large-scale loyalty system using \textbf{Spring Boot, Angular, Kafka, and JOOQ}.
    \item Designed an \textbf{event-driven architecture} and refactored microservices to adopt the \textbf{Listen to Yourself} pattern.
    \item Led the development of an authentication and authorization layer using \textbf{Keycloak and OAuth2}.
    \item Implemented \textbf{CI/CD pipelines}, wrote \textbf{unit tests}, and created detailed documentation.
    \item Provided mentorship to junior engineers and conducted technical meetings with stakeholders.

\end{itemize}


\subsubsection*{Credit Lending For Unsecured Individual \textbar{} AlexBank - Egypt (Nov 2021 - Feb 2023)}
\begin{itemize}
    \item Developed a \textbf{credit lending process management system} for a major bank in Egypt.
    \item Led the migration from \textbf{IBM BPM to BAW}, resolving complex debugging challenges.
    \item Automated testing using \textbf{UI Path RPA, SOAP UI, and Excel-driven test cases}.
    \item Built BPM dashboards to \textbf{debug production issues efficiently}.
    \item Promoted to \textbf{Software Engineer in early 2023}, leading the project for its final six months.
\end{itemize}

\subsubsection*{Mobile App Life Insurance \textbar{} AXA - Egypt (Sep 2023 – Nov 2023)}
\begin{itemize}
    \item Worked on a \textbf{change request (CR)} for a global insurance company's mobile app built with \textbf{Ionic and Java Liferay}.
    \item Designed and implemented life insurance claims integration, working with \textbf{Atlassian API}.
    \item Addressed complex challenges in \textbf{Jira ticket automation} to optimize customer workflow.
\end{itemize}

\subsection*{Static Website development \textbar{} Freelance (August 2020 – Oct 2021)}
\begin{itemize}
    \item Developed front-end applications using \textbf{React} and worked on several \textbf{WordPress} projects.
    \item Delivered a full-fledged \textbf{e-commerce website using Shopify} for a startup, \textbf{Prodo} (Nov 2020 – Feb 2021).
\end{itemize}

\section*{{\faGraduationCap} Education}
\textbf{Bachelor's Degree in Computer Engineering (2020)}

\section*{{\faBook} Other Certifications \& Learning}
\begin{itemize}
    \item \textbf{AWS, Docker, Kubernetes, Kafka, System Design} (Self-taught, personal projects)
    \item \textbf{Data Engineering \& Python} (Learning \& hands-on experimentation)
\end{itemize}
\end{document}